---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# pinkpatheR

A single function R package, for retrieving the absolut path to home directory, in a user agnostic. os agnostic manner. It is handy if all team members use Dropbox or similar cloud service, the absolut path can be constructed utilizing a soft-coded approach; constructing the path by detecting home directory with ```pinkpatheR()``` and bulding the constant parts of the path on top using ```paste0()```.


## Installation

Currently, ```{pinkpatheR}``` is only used in-house, so if you could get your hands on the R-package folder, do the following to install package:
Set as working directory the parent directory of the package, then install.
Use just this once the hardcoded (ew!) string building route until you have ```pinkpatheR```!

```{r eval=FALSE}
setwd("C:/Users/bruno/Dropbox/")
install("pinkpatheR")
```

You should be good to go!

## Example

This is a basic example which shows you how to use ```pinkpatheR``` to retrieve the home directory absolut path:

```{r example}
homedir = pinkpatheR::pinkpatheR()
print(homedir)
```

I have checked using ```goodpractice::gp()``` if the package is okey-ish:
```{r}
goodpractice::gp("pinkpatheR")
```
It will work for the most part - some itchy bugs may kick in but oh well! First ever R package success, I'll call it.
